### 2018-12-07 README.Rmd
update object names in README

```r
> library(areal)
>
> race <- stlRace
> wards <- stlWards
>
> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
# A tibble: 28 x 5
   OBJECTID  WARD       AREA TOTAL_E WHITE_E
 *    <dbl> <int>      <dbl>   <dbl>   <dbl>
 1        1     1  46138761.   7992.    153.
 2        2     2 267817711.  12145.   1323.
 3        3     3  66291644.   7344.    591.
 4        4     4  53210707.   8458.    160.
 5        5     5  60462396.   8783.   1526.
 6        6     6  64337271.  14050.   5840.
 7        7     7 101268146.  15840.   8220.
 8        8     8  45966410.  12188.   7604.
 9        9     9  73993891.  14217.   6838.
10       10    10  62915358.  11239.   8703.
# ... with 18 more rows
```

>>>>

```r
> library(areal)
>
> race <- aw_stl_race
> wards <- aw_stl_wards
>
> aw_interpolate(wards, tid = WARD, source = race, sid = "GEOID", output = "tibble", "TOTAL_E", "WHITE_E")
# A tibble: 28 x 5
   OBJECTID  WARD       AREA TOTAL_E WHITE_E
 *    <dbl> <int>      <dbl>   <dbl>   <dbl>
 1        1     1  46138761.   7992.    153.
 2        2     2 267817711.  12145.   1323.
 3        3     3  66291644.   7344.    591.
 4        4     4  53210707.   8458.    160.
 5        5     5  60462396.   8783.   1526.
 6        6     6  64337271.  14050.   5840.
 7        7     7 101268146.  15840.   8220.
 8        8     8  45966410.  12188.   7604.
 9        9     9  73993891.  14217.   6838.
10       10    10  62915358.  11239.   8703.
# ... with 18 more rows
```
